---
title: "Final Presentation"
author: "Author: Juldyz Woodis"
date: "`r format(Sys.time(), '%B %d, %Y @ %I:%M %p')`"
output: ioslides_presentation
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

## Packages I Used Used

I used ggplot2 for data manipulation and plotting.

```{r, echo = TRUE}
library(ggplot2)
```


## Growth of Tesla Over The Years

I created my dataset using information I found On Kaggle regarding the highs and lows of the Tesla stock. I thought it'd be interesting to research what has become the mogul company of our generation.  [ Tesla Dataset( https://www.kaggle.com/datasets/jillanisofttech/tesla-stock-price?resource=download)

The dataset was last updated on April 11th 2022, so some values may have been added since then. 

**Variables used in the Dataset Manipulations:**

* `High`: Highest stock price of the day
* `Low`: Lowest stock price of the day
* `Open`: Opening price
* `Close`: Closing price adjusted for splits and dividends



```{r}
library(readr)
TSLA_data <- read_csv("TSLA.csv")

```

##


```{r, fig.align = "center", fig.width = 7.5}
library(ggplot2)

ggplot(TSLA_data, aes(Low,High)) + geom_point(aes(x = Open, y = Close, color = '#00BC59' )) + scale_x_discrete(labels = c("Highest Stock Price of The Day", "Lowest Stock Price of The Day")) +    scale_y_continuous(breaks = seq(from = 40, to = 1000, by = 150)) +
  scale_fill_brewer(palette = "Blues") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 10),
    axis.title.y = element_text(size = 12),
    panel.grid.major.x = element_blank(),
    legend.position = "none"
  ) +
 labs(
title = "Tesla's Growth In Stock Prices Over The Years",  subtitle = "Data includes Stock Dates From 2019 To 2022")
```


##

```{r, fig.align = "center", fig.width = 7.5}
ggplot(TSLA_data, aes(Open, Volume)) + geom_point() +
  scale_y_continuous(
    breaks = seq(from = 0, to = 4000, by = 1000))+
  scale_fill_brewer(type = "seq",
  palette = 1,
  direction = 1
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 10),
    axis.title.y = element_text(size = 12),
    panel.grid.major.x = element_blank()
  ) +
  labs(
    title = "Opening Price Compared To Volume Of Purchases",
    subtitle = "Data includes all Opening Prices From 2019 to 2022",
    caption = "*This Is Current Only To April of 2022",
    x = "Price of Stock At Open",
    y = "Volume Of Purchases At Open",
    fill = NULL
  )
```

## What's The Impact Of the Data?

The data showcases what popularity and marketing can do for a company over the years. At the same time we also see the affordability of the stock decreasing as time goes on due to the popularity and marketing. 
